Dissertation reading notes

### 2023-07-14 Texfiles/Draft1.tex
added a small data section

@@

I first solve a modified retirement lifecycle model. Retirees face
\begin{equation*}
      E(U) = \sum_{t = x}^{110 - w}[u(c_{t})]
\end{equation*}

>>>>

\subsection{Data}
The main data set I use is the English Longitudinal Study of Ageing (ELSA) \cite{main_elsa_citation}. ELSA repeatedly interviews
individuals over the age of 50 and asks them a range of questions relating to their income and wealth as well as expectations about
the future. Importantly it also includes detailed information pensions including the type of pension that an individual holds when
working, thus I am able to distinguish between individuals who have defined benefit and defined contribution pensions. For ease of access
I use Harmonized ELSA \footnote{"This analysis uses data or information from the Harmonized ELSA dataset and Codebook, Version G.2 as of
      July 2021 developed by the Gateway to Global Aging Data. The development of the Harmonized ELSA was funded by the National
      Institute on Aging (R01 AG030153, RC2 AG036619, R03 AG043052). For more information,
      please refer to https://g2aging.org/.”} which ensures that variables are comparable across waves. Since this only includes a
subset of the questions in ELSA I also supplement it with variables taken directly from the data.

I also use ONS life tables data.

I also use annuitant life tables data.

I also use FCA product data.

@@

I first solve a modified retirement lifecycle model. The problem that retirees face is as follows:
\textbf{This is not correct -- need to include probs}
\begin{equation*}
      E(U) = \sum_{t = x}^{110 - w}[u(c_{t})]
\end{equation*}
subject to their budget constraint
\begin{equation*}
      c_{t} =a_{t}(1 +r) + p_{t} + ann_{t} -  a_{t+1}
\end{equation*}
where $a_{t}$ are asset holdings in time t, $p_{t}$ is state pension income in time t, and $ann_{t}$ is annuity
income in time t. I use the standard CRRA utility function.
\begin{equation*}
      u(c_{t}) = \frac{c_{t}^{1 - \sigma}}{1 - \sigma}
\end{equation*} In some specifications retirees can leave bequests, I use the bequest function from
\cite{lockwood_red_2012}.
\begin{equation*}
      u(b_{t}) = (\frac{m}{1 - m})^{\sigma}  \frac{((\frac{m c_{0}}{1 - m}) + b_{t})^(1 - \sigma)}{(1 - \sigma)}
\end{equation*}
Where $b_{t}$ is the amount left at death, $m$ is a measure of bequest motive strength and $c_{0}$ is
a minimum amount of consumption that individuals want. \textbf{Check this}

I solve the retirees problem using backward induction. At age 110 there is certainty of death so any leftover assets
are carried over into the next period and bequested. This means that the value at the end of the final period is
either 0 (if we do not allow a bequest motive) or the value of bequests. I then take this value function and solve
an individuals final period problem, choosing assets next period (i.e. those to bequest) and how much to consume.

Using the optimal policy function in the last period, I calculate the value of the last period, which the utility
function and the value function evaluated at the maximum. This is then used in the problem the year before that.
I repeat this process back to the age of retirement to obtain optimal consumption amounts for each year of retirement
and associated value functions.

To simulate the ELSA data I solve this retirement problems for each new retiree in the data set.

### 2023-07-14 Texfiles/Notes.tex
Mainly creating subjective life tables
added a small data section

      \item Got CMI access.
\end{itemize}

>>>>

    \item Got CMI access.

    \item To do: \begin{enumerate}
              \item Start regression work - done
              \item Finish making subjective survival curves - on their way
              \item Finish lit review - done
              \item Start methodology section - need to do
              \item Write couple code - need to do
              \item Write behaviourel model code need to do
              \item Run lifecycle models with different starting points - this is to do.
                    Do we have size of pension though? No. Only size of income.

                    \item Do I want to add defined pension income to the model? Yes I think so. 
          \end{enumerate}
\end{itemize}
